---
title: "causaldraw_annotations analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(tidyr)
library(dplyr)
library(ggrepel)
# detach(package:dplyr)
# detach(package:plyr)
library(ggplot2)
library(stringr)
require(tidyboot)
require(wesanderson)
```

## Load in and preprocess data
```{r message = FALSE}
orig_data <- read_csv("../results/csv/causaldraw_annotations_processed_data.csv") 
orig_survey <- read_csv("../results/csv/causaldraw_annotations_processed_survey_data.csv")
```

## Initial exclusion checks
```{r message=FALSE}
##Preprocessing
#how many participants have been run?
totalrun <- length(unique(orig_data$gameID))
glimpse(totalrun)

#reorder by gameID
orig_data <- orig_data[order(orig_data$gameID),]

#remove too short strokes, unintelligible strokes, "light" elements because participants had been asked to NOT draw the light
cleanup <- orig_data %>%
  filter(!(roi_labelName %in% c("short"))) %>%
  filter(!(roi_labelName %in% c("unintelligible"))) %>%
  filter(!(roi_labelName %in% c("light")))

# cleanup <- orig_data

#how many participants did not complete the full data session?
checkcomplete <- orig_data %>%
  group_by(gameID) %>%
  summarise(count = n_distinct(trialNum))

incompleteSubs <- subset(checkcomplete, count != 11)
glimpse(incompleteSubs)
glimpse(length(unique(incompleteSubs$gameID)))

#how many participants before exclusion (paid)
totalpaid <- totalrun - length(unique(incompleteSubs$gameID))
glimpse(totalpaid)

#how many participants did not complete the catch trial? (remove these data sessions)
checkallowed <- orig_data %>%
  group_by(gameID, catch) %>%
  summarise(count = n_distinct(trialNum))

checking <- checkallowed %>% 
  filter(all(c(TRUE, FALSE) %in% catch))

missingcatch <- setdiff(orig_data$gameID,checking$gameID)
missingcatch <- as.data.frame(missingcatch)
colnames(missingcatch)[1] <- "gameID"
glimpse(missingcatch)
glimpse(length(missingcatch$gameID))
#remove incomplete sessions
cleanup <- cleanup[!(cleanup$gameID %in% missingcatch$gameID),]

#check how many participants?
length(unique(cleanup$gameID)) 

#did any participants speed click through the test trials?
responsespeed <- aggregate(timeResponseLatency ~ trialNum * gameID, orig_data, mean)
responsespeed$seconds <- responsespeed$timeResponseLatency/1000
responsespeed$check <- ifelse(responsespeed$seconds < 0.5, TRUE, FALSE)
speedclicking <- TRUE %in% responsespeed$check
glimpse(speedclicking)
speedyones <- subset(responsespeed, seconds < 0.5)
glimpse(speedyones)
glimpse(length(unique(speedyones$gameID)))

#remove speedy sessions
cleanup <- cleanup[!(cleanup$gameID %in% speedyones$gameID),]

#check how many participants?
length(unique(cleanup$gameID)) 

### remove data sessions with reported technical problems ("5132-439a7475-60b4-41cb-875d-9899392f6edf")
cleanup <- cleanup %>%
  filter(!(gameID %in% c("5132-439a7475-60b4-41cb-875d-9899392f6edf")))
  
#check how many participants?
length(unique(cleanup$gameID)) 
  
#is strokeIndex incrementing properly?
checkordered <- orig_data %>%
  group_by(gameID, sketchID, trialNum) %>%
  summarize(result = all(diff(strokeIndex) == 1)) %>%
  ungroup()
isordered <- FALSE %in% checkordered$result
#if false, then strokeIndex is incrementing properly
glimpse(isordered)

#cleanup environment
rm(checkordered, isordered, speedclicking, responsespeed, checkcomplete, checking, checkallowed, incompleteSubs, orig_data1, orig_data2, orig_data3)
```

## Generate dataframes
```{r message = FALSE}
#add for combinations of causal, functional, and symbols
combo_key <- cleanup %>% 
  distinct(causal, functional, symbol) %>% 
  mutate(combo_id = 1:n()) 

cleanup <- cleanup %>%
  inner_join(combo_key, by = c("causal", "functional", "symbol"))

#extract test trials
data <- cleanup %>% 
    filter(!(catch %in% c(TRUE))) %>% 
    group_by(orig_gameID, sketchID, condition)

#how many participants?
length(unique(data$gameID)) 

#extract catch trials
data.catch <- cleanup %>% 
  filter(catch %in% c(TRUE)) %>% 
  group_by(orig_gameID, sketchID, condition)

#cleanup environment
rm(combo_key)
```

## Apply filtering based on catch trial performance
```{r message = FALSE}
#load in reference dataframes
#all catch trials are "depictive" sketches
reference_A <- read_csv("../results/csv/causaldraw_annotations_label_data_gears1reference.csv")
reference_B <- read_csv("../results/csv/causaldraw_annotations_label_data_gears2reference.csv")
reference_C <- read_csv("../results/csv/causaldraw_annotations_label_data_levers1reference.csv")
reference_D <- read_csv("../results/csv/causaldraw_annotations_label_data_levers2reference.csv")
reference_E <- read_csv("../results/csv/causaldraw_annotations_label_data_pulleys1reference.csv")
reference_F <- read_csv("../results/csv/causaldraw_annotations_label_data_pulleys2reference.csv")

data.catch <- as.data.frame(data.catch)
reference_A <- as.data.frame(reference_A)
reference_B <- as.data.frame(reference_B)
reference_C <- as.data.frame(reference_C)
reference_D <- as.data.frame(reference_D)
reference_E <- as.data.frame(reference_E)
reference_F <- as.data.frame(reference_F)

#give unique identifier for annotations to handle order of strokes
data.catch$value <- paste(data.catch$strokeIndex, data.catch$roi_labelName, data.catch$roi_labelNum, sep = '_')
reference_A$value <- paste(reference_A$strokeIndex, reference_A$roi_labelName, reference_A$roi_labelNum, sep = '_')
reference_B$value <- paste(reference_B$strokeIndex, reference_B$roi_labelName, reference_B$roi_labelNum, sep = '_')
reference_C$value <- paste(reference_C$strokeIndex, reference_C$roi_labelName, reference_C$roi_labelNum, sep = '_')
reference_D$value <- paste(reference_D$strokeIndex, reference_D$roi_labelName, reference_D$roi_labelNum, sep = '_')
reference_E$value <- paste(reference_E$strokeIndex, reference_E$roi_labelName, reference_E$roi_labelNum, sep = '_')
reference_F$value <- paste(reference_F$strokeIndex, reference_F$roi_labelName, reference_F$roi_labelNum, sep = '_')

#combine reference dataframes into one dataframe & check orig values against reference values (e.g., TRUE if matching)
check.data.catch <- mget(paste0('reference_', c('A', 'B', 'C', 'D', 'E', 'F'))) %>%
   bind_rows() %>%
   right_join(data.catch, by = 'sketchID') %>%
   group_by(gameID = gameID.y, sketchID, toy_id = toy_id.y, value = value.y) %>%
   summarise(check = any(value.x == value.y))

check.data.catch$check <- as.logical(check.data.catch$check)

#calculate mean of TRUE/FALSE for each participant's catch trial
catcher <- aggregate(check~gameID + sketchID + toy_id, check.data.catch, mean)

#if catch trial included 2 or more errors, give FALSE for catch trials that fail to pass inclusion criteron
catcher$pass <- ifelse(catcher$toy_id=="gears_1" & catcher$check > ((length(reference_A$roi_labelName) - 3)/length(reference_A$roi_labelName)), TRUE,
                    ifelse(catcher$toy_id=="gears_2" & catcher$check > ((length(reference_B$roi_labelName) - 3)/length(reference_B$roi_labelName)), TRUE,
                    ifelse(catcher$toy_id=="levers_1" & catcher$check > ((length(reference_C$roi_labelName) - 3)/length(reference_C$roi_labelName)), TRUE,
                    ifelse(catcher$toy_id=="levers_2" & catcher$check > ((length(reference_D$roi_labelName) - 3)/length(reference_D$roi_labelName)), TRUE,
                    ifelse(catcher$toy_id=="pulleys_1" & catcher$check > ((length(reference_E$roi_labelName) - 3)/length(reference_E$roi_labelName)), TRUE,
                    ifelse(catcher$toy_id=="pulleys_2" & catcher$check > ((length(reference_F$roi_labelName) - 3)/length(reference_F$roi_labelName)), TRUE,
                        FALSE))))))

#extract catch trials that fail to pass
caughtlowcatches <- subset(catcher, pass == FALSE)
glimpse(length(unique(caughtlowcatches$gameID)))

#remove all data sessions that contained failed catch trials
data <- data[!(data$gameID %in% caughtlowcatches$gameID),]

#how many participants?
length(unique(data$gameID))

#cleanup environment
rm(catcher, check.data.catch, reference_A, reference_B, reference_C, reference_D, reference_E, reference_F)
```
```{r}
#remove participants that did the orig causaldraw
data <- data %>%
  filter(!(wID %in% c("AVBRJBJONL47I")))

# check <- orig_data11 %>% 
  # filter((gameID %in% c("0495-db5fa7cd-9b89-48bc-95aa-bc8f0fdb76d3")))
```

## Inspect dataframe
```{r}
##provide meaningful labels to strokes
#note that `background` will also include strokes depicting the light bulb
data <- data %>% 
  mutate(strokeType = ifelse((causal == TRUE) & (functional==TRUE) & (symbol==FALSE), 'causal',
                        ifelse((causal == FALSE) & (functional==TRUE) & (symbol==FALSE), 'functional',
                        ifelse((causal == FALSE) & (functional==FALSE) & (symbol==TRUE), 'symbol',
                               'background')))) 

data %>%
  group_by(toy_id, condition, strokeType) %>%
  summarize(N=n())
```

## Inspect sketches
```{r}
#how many unique sketches have we annotated? there should be 300 total
length(unique(data$sketchID))

sketchesrun <- list(unique(data$sketchID))
sketchesrun <- as.data.frame(sketchesrun)
colnames(sketchesrun)[1] <- "sketches"

allsketches <- read_csv("../results/csv/allsketches.csv") 

#extract which sketches are not been run yet
missingsketches <- setdiff(allsketches,sketchesrun)
glimpse(missingsketches)

#have all sketches been annotated at least 3 times? (note to self: removed batch_id_across machines, because batch_id's of pilots after '5' will not match the previous batches)
sketchcount <- data %>% 
  group_by(sketchID) %>% 
  summarise(count = n_distinct(gameID))
hist(sketchcount$count)

sketchcount$check <- ifelse(sketchcount$count < 3, TRUE, FALSE)
needmore <- subset(sketchcount, count < 3)
glimpse(needmore)
# write.csv(exportneed,'../stimuli/causaldraw_annotations_patch.csv', row.names = FALSE)

need1 <- subset(needmore, count == 2)
need2 <- subset(needmore, count == 1)
length(sketchcount$sketchID)

toomany <- subset(sketchcount, count > 3)
glimpse(toomany)
```

## Inspect batches
```{r}
#how many unique batches have we run? there should be 30 total
length(unique(data$batch_id_across_machines))

#make dataframe of all batches that have been run
batchesrun <- list(unique(data$batch_id_across_machines))
batchesrun <- as.data.frame(batchesrun)
colnames(batchesrun)[1] <- "batches"

#make dataframe of all batches that should be run
batches <- c("gears_1_batch_0","gears_1_batch_1","gears_1_batch_2","gears_1_batch_3","gears_1_batch_4",
              "gears_2_batch_0","gears_2_batch_1","gears_2_batch_2","gears_2_batch_3","gears_2_batch_4",
              "levers_1_batch_0","levers_1_batch_1","levers_1_batch_2","levers_1_batch_3","levers_1_batch_4",
              "levers_2_batch_0","levers_2_batch_1","levers_2_batch_2","levers_2_batch_3","levers_2_batch_4",
              "pulleys_1_batch_0","pulleys_1_batch_1","pulleys_1_batch_2","pulleys_1_batch_3","pulleys_1_batch_4",
              "pulleys_2_batch_0","pulleys_2_batch_1","pulleys_2_batch_2","pulleys_2_batch_3","pulleys_2_batch_4")
allbatches <- as.data.frame(batches)

#extract which batches are not been run yet
missingbatches <- setdiff(allbatches,batchesrun)
glimpse(missingbatches)
```

## Remove excess annotators
```{r}
#subset sketches that have been annotated by 3 and only first 3 annotators
final_data <- data %>%
  group_by(sketchID) %>%
  mutate(count = match(gameID, unique(gameID))) %>%
  filter(count <= 3)

write.csv(final_data, '../results/csv/causaldraw_annotation_final_data.csv')
# write.csv(final_data, '../results/csv/causaldraw_annotation_final_all_svg_data.csv')
# write.csv(final_data, '../results/csv/causaldraw_annotation_final_svg_data.csv')

glimpse(unique(final_data$roi_labelName))
```

#post-demographic analysis
```{r}
## count gender 
# note to self: combine by aID because old bug prevented gameID collection in one of the survey plugins (this is not a problem for later studies)
sketches_survey <- merge(final_data, orig_survey, by = c("aID"))

#preprocessing
processed <- sketches_survey %>%
  separate(responses, c("participantSex", "judgedDifficulty"), ":", remove = FALSE)

#make text pretty
processed$judgedDifficulty <- substr(processed$judgedDifficulty,2,2) 
colnames(processed)[which(names(processed) == "judgedDifficulty")] <- "gender"

#count
count_gender <- processed %>% 
  filter(gender %in% c("F", "M", "N"))
count_gender_ <- count_gender[!duplicated(count_gender$aID),]
table(count_gender_$gender)

 ## calculate mean age
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

processed <- processed %>%
  separate(responses, c("participantAge", "participantComments"), ",", remove = FALSE)
processed$DOB <- substrRight(processed$participantComments,5) 
processed$DOB <- substr(processed$DOB,1,4) 
calc_age <- processed[grep('^[0-9]', processed$DOB),]
calc_age$DOB <- as.numeric(calc_age$DOB)
calc_age_ <- calc_age$DOB
calc_age_ <- as.data.frame(calc_age_)
colnames(calc_age_) <- c("DOB")
calc_age_$DOT <- 2020
calc_age_ <- na.omit(calc_age_)
calc_age_$age <- calc_age_$DOT - calc_age_$DOB
mean(calc_age_$age)
```


```{r}
#export list of workerIDs
length(unique(final_data$wID))

causaldraw_annotations_workerID <- as.data.frame(unique(final_data$wID))
colnames(causaldraw_annotations_workerID)[1] <- "workerID"

causaldraw_workerID <- read_csv('../results/csv/causaldraw_workerID.csv')
checkDupes <- intersect(causaldraw_workerID$workerID, causaldraw_annotations_workerID$workerID)
checkDupes
````

## Inspect exclusions
```{r}
#how many did we need to exclude from the total ran?
totalrun - length(unique(data$gameID))

#how many did we need to exclude from the total paid?
totalpaid - length(unique(data$gameID))

#percentage excluded from the total ran?
(totalrun - length(unique(data$gameID)))/totalrun

#percentage excluded from the total paid?
(totalpaid - length(unique(data$gameID)))/totalpaid

#cleanup environment
rm(sketchcount, needmore, toomany, cleanup)
```

## Visualize ALL drawn elements, broken down by toy_id
### (numStrokes)
```{r}
#calculate proportion for all drawn elements
props.toys <- final_data %>% 
  group_by(toy_id, condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(toy_id, condition) %>% 
  mutate(proportion=N/sum(N))

#plot proportion
props.toys.plot <- props.toys %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType)) +
  geom_bar(stat="identity") +
  facet_grid(.~toy_id) +
  ggtitle("Number of strokes") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) 

props.toys.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_bytoys_proportion.pdf', height = 18, width = 20, units = 'cm', useDingbats = F)
```

## Collapse across toy_ids
```{r}
#calculate proportion for all drawn elements
props <- final_data %>% 
  group_by(condition, strokeType) %>%
  summarise(N=n()) %>%
  mutate(proportion=N/sum(N))

#plot proportion
props.plot <- props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion) )) +
  geom_bar(stat="identity") +
  ggtitle("Number of strokes") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

props.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_proportion.pdf', height = 18, width =8, units = 'cm', useDingbats = F)
```
#### diff colors, formatting for cogsci
```{r}
#calculate proportion for all drawn elements
props <- final_data %>% 
  group_by(condition, strokeType) %>%
  summarise(N=n()) %>%
  mutate(proportion=N/sum(N))

# make plot
props.plot <- props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.03f", proportion))) +
  geom_bar(stat="identity") +
  xlab("condition") +
  ylab("proportion") +
  scale_x_discrete(labels=c("depict", "explain")) +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +  
  theme(text = element_text(size = 4),
        axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 9),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none") +
  # geom_text(size = 3, position = position_stack(vjust = 0.5))
  geom_text(size = 2, position = position_stack(vjust = 0.5))

props.plot + scale_fill_manual(values = c("#7F96AC", "#63948C", "#9FC8B7", "#F4D79F"))

# ggsave('../results/plots/causaldraw_strokeType_proportion.pdf', height = 9, width = 5,  units = 'cm', useDingbats = F)
ggsave('../results/plots/causaldraw_strokeType_proportion.pdf', height = 8, width = 3,  units = 'cm', useDingbats = F)
```


## Visualize ALL Drawn Elements, broken down by toy_id
### (arcLength)
```{r}
arc.prop.toys <- final_data %>%
  group_by(toy_id, condition, strokeType) %>%
  summarise(totalsum = sum(arcLength)) %>%
  mutate(proportion = totalsum/sum(totalsum))

arc.prop.plot <- arc.prop.toys %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion))) +
  geom_bar(stat="identity") +
  ggtitle("Amount of ink") +
  xlab("condition") +
  ylab("proportion") +
  facet_grid(.~toy_id) +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5))

arc.prop.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_arcLength_bytoys_proportion.pdf', height = 18, width = 20,  units = 'cm', useDingbats = F)
```

## collapse across toy_ids
```{r}
arc.prop <- final_data %>%
  group_by(condition, strokeType) %>%
  summarise(totalsum = sum(arcLength)) %>%
  mutate(proportion = totalsum/sum(totalsum))

arc.prop.plot <- arc.prop %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion))) +
  geom_bar(stat="identity") +
  ggtitle("Amount of ink") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

arc.prop.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_arcLength_proportion.pdf', height = 18, width = 8,  units = 'cm', useDingbats = F)
```

```{r}
#raw count of elements
rawcount.plot <- final_data %>% 
  ggplot(aes(x=condition, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid(.~toy_id) +
  # facet_grid(gameID~toy_id) +
  xlab("Condition") +
  ylab("Raw Count") +
  theme_light()

rawcount.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## Visualize ONLY "entity" elements, i.e., causal and functional
### (numStrokes)
```{r}
#remove non-entity elements
onlyentities <- final_data %>% 
  filter(!(roi_labelName %in% c("symbols"))) %>% 
  filter(!(roi_labelName %in% c("background"))) %>% 
  filter(!(roi_labelName %in% c("light")))
# unique(onlyentities$roi_labelName)

#calculate proportion for entity elements
entity.props.toys <- onlyentities %>% 
  group_by(toy_id, condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(toy_id, condition) %>% 
  mutate(proportion=N/sum(N))

#plot proportion
entity.props.toys.plot <- entity.props.toys %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType)) +
  geom_bar(stat="identity") +
  facet_grid(.~toy_id) +
  xlab("condition") +
  ylab("proportion") +
  theme_light()

entity.props.toys.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_entitytoys_proportion.pdf', height = 18, width = 20,  units = 'cm', useDingbats = F)
```

## collape across toy_id
```{r}
#plot proportion
entity.props <- onlyentities %>% 
  group_by(condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(condition) %>% 
  mutate(proportion=N/sum(N))

entity.props.plot <- entity.props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion))) +
  geom_bar(stat="identity") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

entity.props.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_entity_proportion.pdf', height = 18, width = 8,  units = 'cm', useDingbats = F)
```

## simple chi-squared test for independence btw condition & causal relevance (pooling all strokes)
```{r}
## convert to counts dataframe 
entityCounts <- entity.props %>%
  mutate(causal=ifelse(strokeType == 'causal', TRUE, FALSE)) %>%
  select(condition,causal,N)
## convert counts to 2x2 contingency table
entityTable <- xtabs(N ~ condition+causal, data=entityCounts)  
## conduct chi-squared test
chisq.test(entityTable)
```

```{r}
#raw count of causal and functional elements
plot.prop2 <- onlyentities %>% 
  ggplot(aes(x=condition, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid (.~toy_id) +
  theme_light()

plot.prop2 + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## Visualize ONLY symbols
### (numStrokes)
``` {r}
#count number of symbol strokes by condition
onlysymbols <- final_data %>% 
  filter(!(strokeType %in% c("causal"))) %>% 
  filter(!(strokeType %in% c("background"))) %>% 
  filter(!(strokeType %in% c("functional")))

#raw count
symbol.plot <- onlysymbols %>% 
  ggplot(aes(x=condition, fill=condition)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid(.~toy_id) +
  xlab("condition") +
  ylab("count") +
  theme_light()

symbol.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## Visualize ONLY symbols and background
### (numStrokes)
``` {r}
#count number of symbol strokes by condition
nonentities <- final_data %>% 
  filter(!(strokeType %in% c("causal"))) %>% 
  filter(!(strokeType %in% c("functional")))

#raw count
nonentity.plot <- nonentities %>% 
  ggplot(aes(x=condition, fill=condition)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid(.~toy_id) +
  xlab("condition") +
  ylab("count") +
  theme_light()

nonentity.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

```{r}
#plot proportion
nonentity.props <- nonentities %>% 
  group_by(condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(condition) %>% 
  mutate(proportion=N/sum(N))

nonentity.props.plot <- nonentity.props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion))) +
  geom_bar(stat="identity") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

nonentity.props.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

```{r}
#calculate proportion of RT for all drawn elements
causaldraw_orig_strokeData <- read_csv('../results/csv/causaldraw_stroke_data_run1.csv')
causaldraw_orig_strokeData <- as.data.frame(causaldraw_orig_strokeData)

#match colnames causaldraw_orig_strokeData and finaldata
#make sketchID
causaldraw_orig_strokeData$toy_id <- paste0(causaldraw_orig_strokeData$toy_type, "_", causaldraw_orig_strokeData$toy_variant)
causaldraw_orig_strokeData$sketchID <- paste0(causaldraw_orig_strokeData$toy_id, ".", causaldraw_orig_strokeData$gameID)

#make strokeIndex
causaldraw_orig_strokeData$strokeIndex <- causaldraw_orig_strokeData$currStrokeNum - 1

processed_orig_strokeData <- causaldraw_orig_strokeData %>% 
  select(c(gameID, endStrokeTime, startStrokeTime, sketchID, strokeIndex))

processed_orig_strokeData$orig_gameID <- processed_orig_strokeData$gameID
processed_orig_strokeData <- processed_orig_strokeData %>% 
  select(-c(gameID))

# merge dataframes
merged_final_data <- merge(final_data, processed_orig_strokeData, by=c("sketchID", "strokeIndex")) 

#cleanup
merged_final_data$orig_gameID <- merged_final_data$orig_gameID.x
merged_final_data <- merged_final_data %>% 
  select(-c(orig_gameID.y))

#calculate RT of original strokes
merged_final_data$totalStrokeTime <- merged_final_data$endStrokeTime - merged_final_data$startStrokeTime

mm <- merged_final_data %>% 
  select(c(gameID, orig_gameID, totalStrokeTime, strokeType, condition, toy_type, roi_labelName, causal, toy_id, sketchID, strokeIndex)) 

mm_onlyentities <- mm %>% 
  filter(!(roi_labelName %in% c("symbols"))) %>% 
  filter(!(roi_labelName %in% c("background"))) %>% 
  filter(!(roi_labelName %in% c("light")))

props_rt <- mm %>% 
  group_by(condition, strokeType) %>%
  summarise(totalsum = sum(totalStrokeTime)) %>%
  mutate(proportion = totalsum/sum(totalsum))

#plot proportion
props.plot_RT <- props_rt %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion) )) +
  geom_bar(stat="identity") +
  ggtitle("drawing time") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

props.plot_RT + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_drawingTime_proportion.pdf', height = 18, width = 8,  units = 'cm', useDingbats = F)
```

```{r}
props_rtMean <- mm %>% 
  group_by(condition, strokeType) %>%
  summarise(mean = mean(totalStrokeTime)) 




#plot proportion
props.plot_rtMean <- props_rtMean %>% 
  ggplot(aes(x=condition, y=mean, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="identity") +
  ggtitle("drawing time") +
  xlab("condition") +
  ylab("raw") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) 

props.plot_rtMean + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

```{r}
#raw count of elements
rawcountRT.plot <- mm %>% 
  ggplot(aes(x=condition, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="count") +
  # facet_grid(.~toy_id) +
  ggtitle("drawing time (raw)") +
  xlab("Condition") +
  ylab("ms") +
  theme_light()

rawcountRT.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## simple chi-squared test for independence btw condition & causal relevance (pooling all strokes)
```{r}
## convert to counts dataframe 
entityCounts <- entity.props %>%
  mutate(causal=ifelse(strokeType == 'causal', TRUE, FALSE)) %>%
  select(condition,causal,N)
## convert counts to 2x2 contingency table
entityTable <- xtabs(N ~ condition+causal, data=entityCounts)  
## conduct chi-squared test
chisq.test(entityTable)
```

## stats models
```{r}
# 1. Do people selectively attend to more causally relevant information in the explanation condition, 
# and therefore, draw a higher proportion of causal elements? 
m1 <- glmer(causal ~ condition + (1 + condition | orig_gameID) + (1 | sketchID) + (1 | toy_type) , family="binomial", data = onlyentities)
summary(m1)
```

```{r}
#check across all data if people draw more mechanical elements
final_data$causalfunction <- ifelse(final_data$strokeType=='causal', TRUE, 
                                    ifelse(final_data$strokeType=='functional', TRUE, 
                                           FALSE))

m_all <- glmer(causalfunction ~ condition + (1 + condition | orig_gameID) + (1 | sketchID) + (1 | toy_type) , family="binomial", data = final_data)
summary(m_all)

m_entities <- glmer(causal ~ condition + (1 + condition | orig_gameID) + (1 | sketchID), family="binomial", data = onlyentities)
summary(m_entities)
```

```{r}
# 2. Do people devote a higher proportion of "ink" to causal elements in the explanation condition?
arc <- final_data %>%
  group_by(orig_gameID, sketchID, condition, toy_type, causal) %>%
  summarise(totalLength = sum(arcLength))

#should we take the log of arc$sum since distribution is log?
# hist(log(arc$totalLength))
arc <- arc %>% 
  mutate(logLength=log(totalLength))

arc %>%
  group_by(condition, causal) %>%
  tidyboot_mean(column = logLength)

m2 <- lmer(logLength ~ condition * causal + (1 + condition | orig_gameID) + (1 | toy_type), data = arc)
summary(m2)
```

``` {r}
# Do people devote shorter or longer strokes to causal elements in the explanation condition?
hist(data$arcLength)
hist(log(data$arcLength))

m3 <- lm(log(arcLength) ~ condition * causal, data = final_data)
summary(m3)
```

```{r}
# 3. Do people use more symbols in the explanation condition?
sym <- final_data %>% 
  group_by(orig_gameID, sketchID, condition, toy_type, causal, roi_labelName) %>% 
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(orig_gameID, sketchID, condition, toy_type, causal, roi_labelName) %>%
  summarise(sum = sum(count)) %>% 
  filter(roi_labelName == "symbols")

m4 <- lmer(sum ~ condition + (1 | orig_gameID) + (1 | toy_type), data = sym)
summary(m4)
```

```{r}
# 3. Do people use more background details in the depictive condition?
target <- c("background")
# target <- c("background", "light")
  
background <- final_data %>% 
  group_by(orig_gameID, sketchID, condition, toy_type, causal, roi_labelName) %>% 
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(orig_gameID, sketchID, condition, toy_type, causal, roi_labelName) %>%
  summarise(sum = sum(count)) %>% 
  filter(roi_labelName %in% target)

m5 <- lmer(sum ~ condition + (1 | orig_gameID) + (1 | toy_type), data = background)
summary(m5)
```

```{r}
#4. Do people more time drawing causal elements in the explanation condition?
m6 <- lmer(log(totalStrokeTime) ~ condition*causal + (1 | orig_gameID) + (1 | toy_type), data = mm_onlyentities)
summary(m6)
```
