---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This is analysis notebook for *causaldraw*. 

## Hypotheses
If participants are more selective when producing informative visual explanations than when producing faithful visual depictions, we hypothesize that visual explanations will contain less detail than visual depictions. 

Specifically:

1. We predict that participants will use less “ink” in their visual explanations vs. visual depictions, measured by the mean pixel intensity of grayscale renderings of sketches produced in each condition.

2. We predict that participants will use fewer strokes in their visual explanations vs. visual depictions, where each stroke is defined as the mark made between the depression of the mouse cursor (“pen down”) and the lifting of the mouse cursor (“pen up”). 

3. We predict that participants will spend less time drawing while producing visual explanations vs. visual depictions, defined as the time elapsed between the initiation of the first stroke and the completion of the final stroke of each sketch.

```{r message = False}
library(tidyverse)
library(lme4)
library(lmerTest)
library(tidyr)
library(dplyr)
library(emmeans)
library(ggeffects)
```

## Load in data
```{r message=False}
#load data - run on mTurk 2020
sketch_dat <- read_csv('../results/csv/causaldraw_sketch_data_run1.csv')
stroke_dat <- read_csv('../results/csv/causaldraw_stroke_data_run1.csv')
pixel_dat <- read_csv('../results/csv/meanpix_run1.csv')
survey_dat <- read_csv('../results/csv/causaldraw_survey_data_run1.csv')

#join pixel data with sketch data
fullsketch_dat <- sketch_dat %>% 
  mutate(new_file_id = str_remove_all(file_id, "ABBA_30"), 
         new_file_id = str_remove_all(new_file_id, "BAAB_30"), 
         new_file_id = paste0(new_file_id, condition)) %>% 
  # left_join(pixel_dat, by = c("gameID", "new_file_id")) %>%
  select(-c(new_file_id))
```

## Exclusion
```{r}
#check if any sketches were drawn with 1 stroke
ifOneStroke = 1 %in% fullsketch_dat$numStrokes

exclude <- fullsketch_dat[((fullsketch_dat$numStrokes == 1)),]
exclude$gameID
exclude$file_id

#remove sketches
fullsketch_dat <- fullsketch_dat[!((fullsketch_dat$numStrokes == 1)),]
#run1
fullsketch_dat <- fullsketch_dat %>% 
  #not a machine-sketch
  filter(!((gameID %in% c("1073-31f69960-6dfc-4e45-9a3c-6d7eaa33103e") & (file_id %in% c("levers_2_BAAB_30"))))) %>% 
  #only 1 stroke
  filter(!((gameID %in% c("7376-6f5f07d7-86c3-4c4c-a052-3634d7755b9d") & (file_id %in% c("pulleys_2_BAAB_30")))))

#check if removed
ifOneStroke = 1 %in% fullsketch_dat$numStrokes

#remove sketches from stroke dataframe (run1)
stroke_dat <- stroke_dat[!((stroke_dat$gameID == '7376-6f5f07d7-86c3-4c4c-a052-3634d7755b9d') & (stroke_dat$file_id == 'pulleys_2_BAAB_30')),]
stroke_dat <- stroke_dat[!((stroke_dat$gameID == '1073-31f69960-6dfc-4e45-9a3c-6d7eaa33103e') & (stroke_dat$file_id == 'levers_2_BAAB_30')),]
```

## Inspect Datasets
```{r}
#how many visual explanations and visual depictions? 
fullsketch_dat$toy_id <- paste(fullsketch_dat$toy_type, "_", fullsketch_dat$toy_variant)
fullsketch_dat$sketch_id <- paste(fullsketch_dat$toy_id, "_", fullsketch_dat$gameID)

exp <- fullsketch_dat %>% 
  filter(condition %in% c("explanatory"))
length(unique(exp$sketch_id))

dep <- fullsketch_dat %>% 
  filter(condition %in% c("depictive"))
length(unique(dep$sketch_id))

#how many total sketches? (expected run1 = 300 from 50 participants)
length(unique(fullsketch_dat$sketch_id))

#how many strokes in explanatory and depictive drawings?
table(stroke_dat$condition)

mean(exp$numStrokes)
mean(dep$numStrokes)
```

```{r}
#export list of workerIDs
length(unique(fullsketch_dat$workerId))

causaldraw_workerID <- as.data.frame(unique(fullsketch_dat$workerId))
colnames(causaldraw_workerID)[1] <- "workerID"

#export run1 causaldraw_workerID
write.csv(causaldraw_workerID,'../results/csv/run1/causaldraw_workerID.csv', row.names = FALSE)
```

#post-demographic analysis
```{r}
## count gender
sketches_survey <- merge(fullsketch_dat, survey_dat, by = c("workerId"))

#preprocessing
processed <- sketches_survey %>%
  separate(responses, c("participantSex", "inputDevice"), ":", remove = FALSE)

#make text pretty
processed$inputDevice <- substr(processed$inputDevice,2,2) 
colnames(processed)[which(names(processed) == "inputDevice")] <- "gender"

#count
count_gender <- processed %>% 
  filter(gender %in% c("M", "F", "N"))
count_gender_ <- count_gender[!duplicated(count_gender$gameID),]
table(count_gender_$gender)


## calculate mean age
processed <- processed %>%
  separate(responses, c("participantAge", "participantComments"), ",", remove = FALSE)
processed$DOB <- substr(processed$participantComments,19,22) 
calc_age <- processed[grep('^[0-9]', processed$DOB),]
calc_age$DOB <- as.numeric(calc_age$DOB)
calc_age$DOT <- 2020
calc_age$age <- calc_age$DOT - calc_age$DOB
mean(calc_age$age)
```

glimpse(fullsketch_dat)

## Analyses
*Number of strokes*
Likewise for numStrokes, we will first attempt to fit the maximal model (see below), and if that fails to converge, specify a simpler model that only contains random intercepts for participants and items.
```{r}
m3 <- lmer(numStrokes ~ condition + (1 + condition | gameID) +  (1 + condition | toy_type) , data = fullsketch_dat)
summary(m3)
```

```{r}
m4 <- lmer(numStrokes ~ condition + (1 | gameID) + (1 | toy_type), data = fullsketch_dat)
summary(m4)
```

### plot of numStrokes
```{r}
## getting predictions
df_numStrokes <- ggpredict(m4, terms = "condition")

## making plot
plot_numStrokes <- ggplot(df_numStrokes, aes(x, predicted, fill=x)) +
  geom_bar(aes(y=predicted), stat="summary", width = .6, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  xlab("condition") +
  ylab("numStrokes") +
  # ylim(0, 25) +
  ylim(0, 30) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")
  
plot_numStrokes + scale_fill_manual(values=c("#919191", "#00766e"))

ggsave('../results/plots/causaldraw_numStrokes.pdf', height = 8, width = 4.25, units = 'cm', useDingbats = F)
```

*3. Drawing time of sketch*
Likewise for drawingTime: 
```{r}
#pick out first stroke of startStrokeTime
calc_first <- stroke_dat %>% 
  group_by(gameID, file_id) %>% 
  summarise_all(first)

#pick out first stroke of endStrokeTime
calc_last <- stroke_dat %>% 
  group_by(gameID, file_id) %>% 
  summarise_all(last)

drawing_time <- merge(calc_first, calc_last, by = c("gameID", "file_id"))
drawing_time$drawingTime <- (drawing_time$endStrokeTime.y - drawing_time$startStrokeTime.x)

#calculate amount of time participants spend on each drawing (in SEC)
drawingTime <- (calc_last$endStrokeTime - calc_first$startStrokeTime)
drawingTime <- as.data.frame(drawingTime)

m5 <- lmer(drawingTime ~ condition.x + (1 + condition.x | gameID) +  (1 + condition.x | toy_type.x), data = drawing_time)
summary(m5)

#if falls to converge
m_time <- lmer(drawingTime ~ condition.x + (1 | gameID) + (1 | toy_type.x), data = drawing_time)
summary(m_time)

#compare both causaldraw batches
m_time_comp <- lmer(drawingTime ~ condition.x + condition.x*replication_type.x + (1 | gameID) + (1 | toy_type.x), data = drawing_time)
summary(m_time_comp)
```

### split by condition
```{r}
### depictive
#pick out first stroke of startStrokeTime
final_data_dep <- stroke_dat %>% 
  filter(condition %in% c("depictive"))

calc_first_dep <- final_data_dep %>% 
  group_by(gameID, file_id) %>% 
  summarise_all(first)

#pick out first stroke of endStrokeTime
calc_last_dep <- final_data_dep %>% 
  group_by(gameID, file_id) %>% 
  summarise_all(last)

drawing_time_dep <- merge(calc_first_dep, calc_last_dep, by = c("gameID", "file_id"))
drawing_time_dep$drawingTime <- (drawing_time_dep$endStrokeTime.y - drawing_time_dep$startStrokeTime.x)

#calculate amount of time participants spend on each drawing (in SEC)
drawingTime_dep <- (calc_last_dep$endStrokeTime - calc_first_dep$startStrokeTime)
drawingTime_dep <- as.data.frame(drawingTime_dep)

mean(drawingTime_dep$drawingTime_dep)

### explanatory
#pick out first stroke of startStrokeTime
final_data_exp <- stroke_dat %>% 
  filter(condition %in% c("explanatory"))

calc_first_exp <- final_data_exp %>% 
  group_by(gameID, file_id) %>% 
  summarise_all(first)

#pick out first stroke of endStrokeTime
calc_last_exp <- final_data_exp %>% 
  group_by(gameID, file_id) %>% 
  summarise_all(last)

drawing_time_exp <- merge(calc_first_exp, calc_last_exp, by = c("gameID", "file_id"))
drawing_time_exp$drawingTime <- (drawing_time_exp$endStrokeTime.y - drawing_time_exp$startStrokeTime.x)

#calculate amount of time participants spend on each drawing (in SEC)
drawingTime_exp <- (calc_last_exp$endStrokeTime - calc_first_exp$startStrokeTime)
drawingTime_exp <- as.data.frame(drawingTime_exp)

mean(drawingTime_exp$drawingTime_exp)
```

### plot for drawing time
```{r}
## getting predictions
df_drawingTime <- ggpredict(m_time, terms = "condition.x")

## making plot
plot_drawingTime <- ggplot(df_drawingTime, aes(x, predicted, fill=x)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  xlab("condition") +
  ylab("drawingTime") +
  ylim(0, 80000) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

plot_drawingTime + scale_fill_manual(values=c("#919191", "#00766e"))

ggsave('../results/plots/causaldraw_drawingTime.pdf', height = 8, width = 4.25, units = 'cm', useDingbats = F)

```

```{r}
#check how long participants take to complete the entire experiment (in MIN)
studyTime <- (fullsketch_dat$time_elapsed/1000)/60
mean(studyTime)
```


## Exploratory Analyses
We also plan to analyze potential differences in reaction time, i.e., period of time between the beginning of trial and when participants make their first stroke. This is motivated by the possibility that if participants in the depictive condition attempt to accurately capture the shape, size, and location of elements, they may begin drawing immediately after the video demonstration before their memory decays, resulting in relatively low reaction times. However, if participants in the explanatory condition attempt to draw how elements relate to each other, they may plan how they will represent this abstract information before beginning their drawing, resulting in relatively high reaction times. 

*4. Reaction time*
```{r}
#calculate when 
firststroke_dat <- stroke_dat %>% 
  group_by(gameID, file_id, startResponseTime) %>% 
  filter(row_number()==1) 

rt <- firststroke_dat$startStrokeTime - firststroke_dat$startResponseTime

m6 <- lmer(rt ~ condition +  (1 + condition | gameID) +  (1 + condition | toy_type), data = firststroke_dat)
summary(m6)
```

``` {r}
#arcLength
m7 <- lmer(arcLength ~ condition + (1 + condition | gameID) +  (1 + condition | toy_type) , data = stroke_dat)
summary(m7)

m8 <- lmer(arcLength ~ condition + (1 | gameID) + (1 | toy_type), data = stroke_dat)
summary(m8)
```






